Discovery of s-process enhanced stars in the LAMOST survey

### 2018-05-23 article/ms.tex
paper

In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis. Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. Most of our barium stars ($69\%$) show strong carbon enhancements, yet, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement. We argue this may have been a selection bias in previous studies. Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars. A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain. Additionally, theoretical models show that this source is dominant in low-mass AGB stars thus, it follows that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.

@@

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates. In Section \ref{sec:methods}, we describe the observations and candidate selection. Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis}, we discuss the properties of our barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety. This stellar sample consists of; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.

For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.

It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 257 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12. However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement. Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star. Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$. Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.

\begin{table*}
\centering
\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features. Only 5/257 barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at the single technetium line 4238\,\AA, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 (available online in its entirety) nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsection{Dynamics}
Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 898 s-process enhanced stars. Utilising the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}. For our Gaia matched sample, we computed spatial velocities and galactic longitude and latitudes. Spatial velocities are relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$). Our analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars. Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 257 barium star candidate sample. The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts. In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and in accordance with previous literature, it can be concluded that our barium star sample is extrinsic. However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement. Additionally, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{yields_test.pdf}
    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates. Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses. Coloured lines red, purple, and brown indicate surface [hs/ls] yields from \citet{karakas_lugaro2016} for [Fe/H] at +0.3. 0.0, and -0.3. From \citet{karakas2018} for [Fe/H] at -0.7, and from \citet{fishlock2014} for [Fe/H] at -1.2.}
    \label{fig:figure3}
\end{figure}

\subsection{Carbon bands}
Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process. In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star. In an identical mechanism to the presence of s-process element enhancement, carbon enhanced stars exist intrinsically or extrinsically. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 257 barium candidates. These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
%Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.

\subsection{Comparison to AGB yields}
AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement. In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 barium stars identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex). Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$. Given our barium stars exist in this metallicity range of 0 to -1.1, we can classify them as CH stars as defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.

@@

The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event. Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated. For our entire 898 sample, the figure shows \% reside within the galactic disk(\% thin disk and \% thick disk ), and \% within the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo. \cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars. Although, excluding \cite{decastro2016}’s sample, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources. However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not large enough to represent the overall galactic position of extrinsic S stars.

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement. This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.  Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars, indicating our barium stars were not produced through an unusual galactic event.

>>>>

In this paper we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis. Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates. Our sample includes; 187 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars which exhibit strontium enhancement only. Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. The majority of our barium stars ($95\%$) show strong carbon enhancements, yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement. We argue this may have been a selection bias in previous studies. Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars. A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain. Additionally, theoretical models show that this source is dominant in low-mass AGB stars thus, it follows that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.

@@

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates. In Section \ref{sec:methods}, we describe the observations and candidate selection. Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis}, we discuss the properties of our barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 895 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety. This stellar sample consists of; 187 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 659 with exclusively strontium enhancement.

For the remainder of this paper we restrict our analysis to the 187 classical `barium stars' stars that show enhancement in both barium and strontium. While the 49 or 659 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.

It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 187 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12. However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement. Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star. Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$. Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.

\begin{table*}
\centering
\caption{Properties of 895 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features. Only 5/187 barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at the single technetium line 4238\,\AA, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 (available online in its entirety) nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/187 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsection{Dynamics}
Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 871/895 Gaia matched s-process enhanced stars. Utilising the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}. For our Gaia matched sample, we computed spatial velocities and galactic longitude and latitudes. Spatial velocities are relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$). Our analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars.

@@

Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars. Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 187 barium star candidate sample. The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts. In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and in accordance with previous literature, it can be concluded that our barium star sample is extrinsic. However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement. Additionally, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{yields_test.pdf}
    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 187 barium star candidates. Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses. Coloured lines red, purple, and brown indicate surface [hs/ls] yields from \citet{karakas_lugaro2016} for [Fe/H] at +0.3. 0.0, and -0.3. From \citet{karakas2018} for [Fe/H] at -0.7, and from \citet{fishlock2014} for [Fe/H] at -1.2.}
    \label{fig:figure3}
\end{figure}

\subsection{Carbon bands}
Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process. In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star. In an identical mechanism to the presence of s-process element enhancement, carbon enhanced stars exist intrinsically or extrinsically. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 187 barium candidates. These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
%Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.

\subsection{Comparison to AGB yields}
AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement. In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 barium stars identified in LAMOST. Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex). Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$. Given our barium stars exist in this metallicity range of 0 to -1.1, we can classify them as CH stars as defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.

@@

The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event. Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated. For our entire 898 sample, the figure shows 97\% reside within the galactic disk(81\% thin disk and 16\% thick disk ), and \% within the halo. Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo. \cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars. Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars. \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources. However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not large enough to represent the overall galactic position of extrinsic S stars.

@@

We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release. From 454,180 giant stars, we identify 895 s-process candidates including: 187 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 659 exhibiting exclusively strontium enhancement. This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.  Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars, indicating our barium stars were not produced through an unusual galactic event.
